Inference methods comparison for the simplified Naomi model using maximum mean discrepancy

### 2023-05-09 src/naomi-simple_mmd/mmd.Rmd
Calculate MMD with kernlab #42

---
title: "Inference methods comparison for the simplified Naomi model using maximum mean discrepancy"
author:
- name: Adam Howes
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background**  We have run the simplified Naomi model using a range of inference methods: `TMB`, `aghq`, `adam` and `tmbstan`.

@@

```{r}
stopifnot(names(tmb$fit$sample) == names(aghq$quad$sample))
stopifnot(names(tmb$fit$sample) == names(adam$adam$sample))
stopifnot(names(tmb$fit$sample) == names(tmbstan$mcmc$sample))
```

## Run details {.tabset}

For more information about the conditions under which these results were generated, see:

### `TMB`

```{r}
dependency_details <- function(i) {
  report_name <- names(depends[[i]])
  print(paste0("Inference results obtained from ", report_name, " with the query ", depends[[i]][[report_name]]$id))
  report_id <- orderly::orderly_search(query = depends[[i]][[report_name]]$id, report_name)
  print(paste0("Obtained report had ID ", report_id, " and was run with the following parameters:"))
  print(orderly::orderly_info(report_id, report_name)$parameters)
}

dependency_details(1)
```

### `aghq`

```{r}
dependency_details(2)
```

### `adam`

```{r}
dependency_details(3)
```

### `tmbstan`

```{r}
tmbstan_details <- dependency_details(4)
tmbstan_details
```

@@

```{r}
#' To write!
```

>>>>

---
title: "Inference methods comparison for the simplified Naomi model using maximum mean discrepancy"
author:
- name: Adam Howes
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background**  We have run the simplified Naomi model using a range of inference methods: `TMB`, `aghq` and `tmbstan`.

@@

```{r}
stopifnot(names(tmb$fit$sample) == names(aghq$quad$sample))
stopifnot(names(tmb$fit$sample) == names(tmbstan$mcmc$sample))
```

@@

```{r}
mmd1 <- kernlab::kmmd(matrix(tmb$fit$sample$beta_rho), matrix(tmbstan$mcmc$sample$beta_rho))
mmd2 <- kernlab::kmmd(matrix(aghq$quad$sample$beta_rho), matrix(tmbstan$mcmc$sample$beta_rho))

mmd1
mmd2
```
